\section{Theoretical background}

\subsection{Hovering Information System}

The hovering information system is composed by two main components: mobile
nodes and pieces of hovering information.

\emph{Mobile nodes} are components moving into the environment with a limited
communication range, capable of communicate to peers, discover neighbors,
access and store (into a limited buffer) pieces of
hovering information. A mobile node is assumed able to determinate its
geographic position, speed and direction.

\emph{Pieces of hovering information} are data that have to \emph{survive}
inside a circular area centered at a location called \emph{anchor location} and
having a radius called \emph{anchor radius}. The survivability goal of a piece
of hovering information is achieved moving or replicating the piece itself
through the mobile nodes. A piece of hovering information may have some
policies controlling the movement between nodes.

In an hovering information system, three main requirements may be defined for each
piece of hovering information \cite{hover}:
\begin{description}
	\item[Survivability:] a piece of hovering information is alive at some time
		$t$, if there is at leas one node hosting a replica of this information.
		\\
		$survivability = \frac{alive\_time}{total\_time}$
	\item[Availability:] a piece of hovering information is available at some time
		$t$, if there is at least one node in its anchor area hosting a replica of
		this information.
		\\
		$avaiability = \frac{avaiable\_time}{total\_time}$
	\item[Accessibility:] a piece of hovering information is accessible by a node
		at some time $t$, if the node is able to get this information; therefore, a
		replica exists in the node communication range.
		\\
		$accessibility = \frac{replica\_covered\_area}{anchor\_area}$
\end{description}

